---
title: "Week-4 Interactive Practice"
author: "Created by: Congyu Hang and Shahriar Shams"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```


## plots using ggplot()

### Question 1

__a).__


```{r echo=FALSE,message=FALSE}
library(tidyverse)
library(gapminder)
library(ggplot2)
library(ggExtra)
data(gapminder)

head(gapminder)
```

In this question, we will use the data set "gapminder" again. Please generate the following plot based on "gapminder". Where "Average Global GDP percap" is the average of "gdpPercap" of all countries for a particular year.


Hint: You might need to generate a new table first. 

```{r echo=FALSE,message=FALSE}
yr_gdp=gapminder %>% select(year,gdpPercap)%>%  group_by(year) %>% summarise(avg.gdp = mean(gdpPercap))
ggplot(yr_gdp,aes(year,avg.gdp))+geom_point()+geom_smooth(method = "lm")+ylab("Average Global GDPpercap")
```
```{r plot1,exercise=TRUE}
library(tidyverse)
library(gapminder)
library(ggplot2)
library(ggExtra)
data(gapminder)

```

```{r plot1-hint}
#d=gapminder %>% (select(...)%>%)  group_by(...) %>% summarise(...)
#
#ggplot(d, aes(...))+geom_point()+geom_smooth(...)
```




\  

\  

__b).__ Please generate the following scatter plot plot based on "gapminder".

Hint: You might need to generate a new table first. And there are two layers: one for the points and one for the lines.


```{r echo=FALSE,message=FALSE}
continent_gdp = gapminder %>% select(year,continent,gdpPercap)%>%  group_by(continent,year) %>% summarise(avg.gdp = mean(gdpPercap))
ggplot(continent_gdp,aes(year,avg.gdp,color=continent))+
  geom_point()+ geom_line()+
  ylab("Average Continental GDPpercap")
```


```{r plot2,exercise=TRUE}
library(tidyverse)
library(gapminder)
library(ggplot2)
library(ggExtra)
data(gapminder)

```

```{r plot2-hint}
#d = gapminder %>% group_by(continent,year) %>% summarise(...)
#
#ggplot(d, aes(...)) + geom_point() + geom_line() + ylab("")
```


\  

\  

__c).__ Please generate the following density plot based on the "lifeExp" variable and a new categorical variable to be created in the following way.

Name:Time Point

If year is between [1952,1967], Time Point=1;

if year is between [1972,1987], Time Point=2;

if year is between [1992,2007], Time Point=3.


```{r echo=FALSE,message=FALSE}
category_yr = gapminder %>% mutate(tp=case_when(year <= 1967 ~ 1,
                                                year >= 1992 ~ 3,
                                                TRUE ~ 2))
ggplot(category_yr,aes(lifeExp))+geom_density(aes(fill = continent),alpha=0.5)+facet_wrap(~tp)+theme(legend.position = "bottom")
```
```{r plot3,exercise=TRUE}
library(tidyverse)
library(gapminder)
library(ggplot2)
library(ggExtra)
data(gapminder)

```

```{r plot3-hint}
#d = gapminder %>% mutate( tp = case_when( ))
#
#ggplot(d, aes(...))+geom_density(...)+facet_wrap(...)
```


## Miscellaneous


### Question 2 Wide Data and Long Data
The code below shows a dataset "d" created manually as the following with 3 individuals and their incomes from three different types of investments.



```{r widedata,echo=T}
library(tidyverse)
d = data.frame("Name" = c("Barbie","Ken","Allan"),
               "Invest.1" = c(6662,5789,6267),
               "Invest.2" = c(10059.0,8749.5,9466.5),
               "Invest.3" = c(17667.2,15117.4,16360.2))

d

```

convert this __wide__ data "d" to __long__ data with a variable called Investment_Type that takes values "Invest.1", "Invest.2" and "Invest.3" and beside this variable there will be another variable that will have the corresponding investment incomes [the resulting dataset will have three variables in total]. 
 
 \  
 
```{r wide,exercise=TRUE}

library(tidyverse)
d = data.frame("Name" = c("Barbie","Ken","Allan"),
               "Invest.1" = c(6662,5789,6267),
               "Invest.2" = c(10059.0,8749.5,9466.5),
               "Invest.3" = c(17667.2,15117.4,16360.2))




```

```{r wide-hint}
# d %>% pivot_longer(cols=...,names_to=...,values_to=...)
```


\  

\  

### Question 3 Matrix Multiplication

We have created a table called demand that contains the number of cups of coffee and the amount of snacks that were paid for during some events. The second table is called Starbucks with the prices of coffee and snacks and the stars customers earn from buying these goods. 

Please use matrix multiplication to show the cost of coffee and amount of stars earned for each event.

```{r matrixdata}
demand = data.frame("Event" = c("A","B","C","D"),
                    "Coffee" = c(550,100,400,440),
                    "Snacks" = c(670,170,500,510))


starbucks = data.frame("Item" = c("Coffee","Snack"),
                   "Price" = c(6.99,2.99),
                   "Stars" = c(20,10))

demand

starbucks
```


```{r matrix, exercise=TRUE}

demand = data.frame("Event" = c("A","B","C","D"),
                    "Coffee" = c(550,100,400,440),
                    "Snacks" = c(670,170,500,510))


starbucks = data.frame("Item" = c("Coffee","Snack"),
                   "Price" = c(6.99,2.99),
                   "Stars" = c(20,10))




```


```{r matrix-hint}
#m1 = as.matrix(demand %>% select(Coffee, Snacks))
#m2 = as.matrix(starbucks %>% select(Price, Stars))

#purchase = m1 %*% m2
```

\  

\  


### Question 4

```{r quiz1}
quiz(
  question("Suppose the matrix that you got with the cost of coffee and amount of stars earned for each event is called 'purchase'. Which of the options will generate the average cost of coffee and average  amount of stars earned per event,select all that apply",
    answer("lapply(list(purchase[,1],purchase[,2]), mean)",correct=TRUE),
    answer("apply(purchase,1,function(x) sum(x)/length(x))"),
    answer("apply(purchase,2,mean)",correct=TRUE),
    answer("apply(purchase,2,function(x) sum(x)/length(x))",correct=TRUE),
    allow_retry = TRUE
  )
)
```
