---
title: "Week-9 Interactive Practice"
author: "Created by: Congyu Hang and Shahriar Shams"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```


## Regression and Plot

In this exercise, we will explore the Temp and Ozone variables in data set "airquality".

\  

### a).

We want to predict Ozone using Temp. Recreate this following scatter plot of these 2 variables with an overlay of the *linear regression* smooth curve. 

```{r w90, echo=F,message=F,warning=F}
library(tidyverse)
library(ggplot2)
data("airquality")

ggplot(airquality,aes(x=Temp, y = Ozone)) +
  geom_point()+
  geom_smooth(method="lm")

```




```{r w91,exercise=TRUE}
library(tidyverse)
library(ggplot2)
data("airquality")
```

```{r w91-hint}
#ggplot(...,aes(...)) +
#  geom_point()+
#  stat_smooth(...)
#m = lm(...)
#summary(m)
```



\  

### b) 

Fit a linear regression model of these 2 variables, report and interpret the coefficients. Based on the regression output and your plot from part(a), do you think the model explains the relationship of the variables well?

\  


```{r w912,exercise=TRUE}
library(tidyverse)
library(ggplot2)
data("airquality")
```

```{r w912-hint}

#m = lm(...)
#summary(m)
```




### c).


Calculate a 95% bootstrap CI for the regression coefficient of the term associated to "Temp".


```{r w95,exercise=TRUE}

```




```{r w95-hint}
#boot_function=function(){
#  boot.d = d %>% sample_n(..., replace=...)
#  m2 = lm(... ~ ,
#           data = boot.d)
#  s = coef(m2)[...]
#  return(s)
#}
#output = replicate(...)
#quantile(..., ...)
```


\  





### d).

Overlay a polynomial regression with highest degree = 2 on a scatter plot. Do you think the quadratic model look better fit than the linear model?


```{r w92,exercise=TRUE}
library(tidyverse)
library(ggplot2)
data("airquality")
```

```{r w92-hint}
#ggplot(...,aes(...)) +
#  geom_point()+
#  stat_smooth(...,formula = ...=...+I(...))
```


\  

### e).

Perform a 5-fold cross validation using the 2nd degree polynomial regression model you used in part d and calculate an average MSE.



```{r w94,exercise=TRUE}
library(tidyverse)
library(ggplot2)
data("airquality")
```

```{r w94-hint}
#d = airquality %>% mutate(group_ind = sample(c(1:5),
#                                  size=nrow(airquality),
#                                  replace = T))
#mse_vec = ...

#for (i in 1:5){
  
#  m2 = lm( ... ~ ,
#           data = d %>% filter(group_ind != i))
  
#  pred_y = predict(..., ... =  d %>% filter(...)   )
  
#  mse_vec[i] = mean(...)^2, na.rm = ...)
  
#}

#mean(...)
```

