---
title: "Week-10 Interactive Practice"
author: "Created by: Congyu Hang and Shahriar Shams"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```


## Categorical Variable Prediction

We will use the data set "swiss" in today's exercise. Please check the descriptions below.

[,1]	Fertility	‘common standardized fertility measure’

\n

[,2]	Agriculture	% of males involved in agriculture as occupation

\n

[,3]	Examination	% draftees receiving highest mark on army examination

\n

[,4]	Education	% education beyond primary school for draftees.

\n

[,5]	Catholic	% ‘catholic’ (as opposed to ‘protestant’).

\n

[,6]	Infant.Mortality	live births who live less than 1 year.


\n


The response variable here is Fertility.

### a).

#### i).Please mutate a binary variable called ftlt, which is equal to 1 when Fertility > 70, otherwise 0.

#### ii).Then mutate group_ind variable for cross validation with proportions 0.6 (training) and 0.4(testing).

#### iii). Use Agriculture, Education and Catholic as predictors and fit a logistic regression model based on the training data and report the parameters and interpret them.


```{r w101,exercise = TRUE}
set.seed(698)
library(tidyverse)
data("swiss")
```

```{r w101-hint}
#...swiss %>% mutate(ftlt = ifelse(...))
#d = d %>% mutate(group_ind = sample(c("train","test"),
#                                    size = ...,
#                                    prob = ...,
#                                    replace = ...))
#d_train = d %>% filter(group_ind == "train")
#d_test = d %>% filter(group_ind == "test")
#logit.mod = glm(...)
```



### b).

Please first copy the code from the previous chunk. Then plot an ROC curve and report the AUC value.

```{r w102,exercise = TRUE}
set.seed(698)
library(tidyverse)
library(pROC)
data("swiss")
```

```{r w102-hint}
#p = predict(...,type = "response",...)
#roc_logit = roc(...)
#ggroc(...)
#auc(...)
```


### c).

Please first copy the code from part a.
You might observe that the coefficient of Education has a slightly higher p-value, please construct a 95% bootstrapping CI based on 1000 replication of this regression coefficient from the model that we estimated previously and interpret. 

```{r w103,warning = FALSE, exercise = TRUE}
set.seed(698)
library(tidyverse)
data("swiss")
```


```{r w103-hint}
#boot_func = function(){
#  boot.d = d_train %>% sample_n(...,replace = ...)
#  m= glm(...)
#  s = coef(m)[3]
#  return(s)
#}
#output = replicate(...)
#quantile(...)
```


### d).


Please first copy the code from part a.
Use the same variables and training set from previous part to build a decision tree and plot it. Also, report your prediction accuracy based on test set.

```{r w104,exercise = TRUE}
set.seed(698)
library(tidyverse)
library(rpart)
library(rattle)
data("swiss")
```

```{r w104-hint}
#rpart(...)
#fancyRpartPlot(...)
#conmat = ...
```


### e).

Please use the initial data swiss and the variables that you used to construct model in previous parts do a 4-fold cross validation and report your average accuracy.

```{r w105,exercise = TRUE}
set.seed(698)
library(tidyverse)
data("swiss")
```

```{r w105-hint}
#for (i in 1:k){
#  m2 = ...
  
#  conmat = ...
#}


```


