---
title: "Week-2 Interactive Practice"
author: "Created by: Congyu Hang and Shahriar Shams"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```


## Vectors and Functions

### Q1

x = c("T", "T", "F")
```{r quiz1}
quiz(
  question("What would be the output of 'class(x)'",
    answer("numeric"),
    answer("logical"),
    answer("integer"),
    answer("character",correct=TRUE),
    allow_retry = TRUE
  )
)
```

\  


### Q2
x = c(2, 6, 7, 9, 8, 10)
```{r quiz2}
quiz(
  question("What would x[c(2,6)] be",
    answer("6 10",correct=TRUE),
    answer("7 9 8 10"),
    answer("NA"),
    answer("2 6"),
    allow_retry = TRUE
  )
)
```


\  


### Q3
x = c(2, 6, 7, 9, 8, 10)

```{r quiz3}
quiz(
  question("which of these following codes will give us 6 and 8 out of this vector?",
    answer("x[c(2,5)]"),
    answer("x[-c(1,3,4,6)]"),
    answer("x[c(FALSE, TRUE, FALSE, FALSE, TRUE, FALSE)]"),
    answer("all of the above", correct=TRUE),
    allow_retry = TRUE
  )
)
```



\  



### Q4

Check the following code and output

```{r vector1,echo=T}
my_func = function(){
  x=3
  return(x)
}
(y = replicate(5,my_func()))
```


how to generate the same output *with one line of code without using y=c(......)*

```{r vec1,exercise=TRUE}

```

```{r vec1-hint}
(y=rep())
```





\  







### Q5
Please read the following code
```{r vector2,echo=T}
v=vector()

for(i in 1:50){
  v[i] = i^2
}
v
```

How to create the object 'v' without using any loop
```{r vec2,exercise=TRUE}

```

```{r vec2-hint}
v = seq()
```

\  



### Q6

Suppose you are playing a game where a fair die is rolled and if it is a six, you win six dollars. If it is 4 or 5 you do not win anything. But if it is 1,2 or 3 you have to pay 1 dollar (you lose). By writing a function that mimics this game, and by replicating the function 10000 times, calculate the expected gain per game (i.e. average).  

(theoretically, the answer should be 0.5 dollar)

```{r vec3,exercise=TRUE,excercise.lines=10}

```

```{r vec3-hint}
# Let, x is the outcome of the die, y is the associated dollar amount
# my_function = function(){
#     x = sample(c(1,2,3,4,5,6),size=1)
#     if(x == ){ 
#       y = 
#     }else if (x %in% c(  )){
#       y = 
#     }else{
#       y = 
#      }
#     return(y)
# }
# replicate( )
# mean()
```










## Introduction to _tidyverse_

In this section we will use the built-in data set mtcars

```{r tdvs1,echo=T,message=F,warning=F}
library(tidyverse);
glimpse(mtcars)
```

```{r tdvs2, echo=T}
head(mtcars)
```

Read this page for a description of the dataset: https://www.rdocumentation.org/packages/datasets/versions/3.6.2/topics/mtcars


\  



### Q1

Write the tidyverse equivalence of the following code.

```{r tdvs3, echo=T}
max(mtcars$mpg[mtcars$gear==5 | mtcars$gear==4])
```


```{r tdvs4, exercise=TRUE}
library(tidyverse)

```

```{r tdvs4-hint}
mtcars %>% filter(gear %in% c(4,5)) %>%summarise(MAX=max(mpg))
```


\  

### Q2
Recreate this following table

```{r tdvs55, echo=F,message=F}
library(tidyverse)
mtcars %>% group_by(cyl,am) %>% summarise(N=n(),AVG_mpg=mean(mpg))
```

(where N is the number of cars/observation in the dataset)



```{r tdvs5, exercise=TRUE,message=F}

```


```{r tdvs5-hint}
#library(tidyverse)
#mtcars %>% group_by( ) %>% summarise(N= ,AVG_mpg= )
```


\  

### Q3
Recreate this following graph using the dataset.

```{r tdvs6, echo=F}
mtcars %>% select( mpg , disp ) %>% plot()
```

```{r tdvs7, exercise=TRUE}

```

```{r tdvs7-hint}
#mtcars %>% select( , ) %>% plot()
```

