---
title: "Week-2 Interactive Practice"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```


## Vectors and Functions

### Q1

x = c("T","T","F")
```{r quiz1}
quiz(
  question("What would the class(x) be",
    answer("numeric"),
    answer("logical"),
    answer("integer"),
    answer("character",correct=TRUE),
    allow_retry = TRUE
  )
)
```

x = c(2,6,7,9,8,10)
```{r quiz2}
quiz(
  question("What would x[c(2,6)] be",
    answer("6 10",correct=TRUE),
    answer("7 9 8 10"),
    answer("NA"),
    answer("2 6"),
    allow_retry = TRUE
  )
)
```

### Q2

Check the following code and output, how to generate the same output *within one line without using y=c(......)*

```{r vector1,exercise=TRUE, exercise.eval=TRUE}
my_func = function(){
  x=3
  return(x)
}
(y = replicate(5,my_func()))
```

```{r vec1,exercise=TRUE}

```

```{r vec1-hint}
(y=rep())
```

### Q3
Please read the following code
```{r vector2,exercise=TRUE, exercise.eval=TRUE}
v=vector()

for(i in 1:50){
  v[i] = i^2
}
v
```

How to create an equivalent output within 2 lines
```{r vec2,exercise=TRUE}

```

```{r vec2-hint}
v = seq()
```

Then please create a plot of v and overlay the derivative of y = x^2 on top of v
```{r vec2-additional,exercise=TRUE}
v=vector()

for(i in 1:50){
  v[i] = i^2
}

```

```{r vec2-additional-hint}
plot(v)
abline(a=0,b=2)
```

## Introduction to tidyverse

In this section we will use the built-in data set mtcars

```{r tdvs1, exercise=TRUE, exercise.eval=TRUE,message=FALSE}
library(tidyverse);
glimpse(mtcars)
```

```{r tdvs2, exercise=TRUE, exercise.eval=TRUE}
library(tidyverse)
head(mtcars)
```

### Q1

For all of the cars whose gear=5, what is the maximum mpg value of them, i.e. write code that is equivalent to the following code

```{r tdvs3, exercise=TRUE, exercise.eval=TRUE}
max(mtcars$mpg[mtcars$gear==5 | mtcars$gear==4])
```
```{r tdvs4, exercise=TRUE}
library(tidyverse)
```

```{r tdvs4-hint}
mtcars %>% filter(gear %in% c(4,5)) %>%summarise(MAX=max(mpg))
```

### Q2
For different combinations of variables vs and am, what are the number of cars and mean of qsec?

```{r tdvs5, exercise=TRUE}
library(tidyverse)
```

```{r tdvs5-hint}
library(tidyverse)
mtcars %>% group_by(vs,am) %>% summarise(N=n(),AVG=mean(qsec))
```

### Q3
Create a plot where x-axis is variable mpg and y-axis is variable disp by extracting the 2 variables and then create plot.

Equivalently, you can plot using the following code
```{r tdvs6, exercise=TRUE, exercise.eval=TRUE}
plot(x=mtcars$mpg,y=mtcars$disp)
```

```{r tdvs7, exercise=TRUE}
library(tidyverse)
```

```{r tdvs7-hint}
library(tidyverse)
mtcars %>% select(mpg,disp) %>% plot()
```

