---
title: "Our First Lesson"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```


## Topic 1: Quiz




```{r quiz1}
quiz(
  question("In which of the following panes the information of created objects such as scalars, vectors or
data-sets, in any session show up?",
    answer("source",message = "The source pane is where you can open/edit code files and save for future use."),
    answer("console",message =  "The console is where you can type in the codes and where R prints the numeric outputs."),
    answer("Environment", correct = TRUE),
    answer("Plots/Help/Files", message = "The Plots/Help/Files pane is where you can toggle between any graphical output,
help pages, or file directories."),
    allow_retry = TRUE
  )
)
```



## Topic 2: Try to do these using for-loop or while loop and/or using if statement.

### a) 1 ∗ 2 ∗ 3 ∗ 4 ∗ ..... ∗ 100 =?

We all know that this is actually 100! and computed by the following expression in r.
```{r factorial,exercise=TRUE, exercise.eval=TRUE}
factorial(100)
```

How can we compute this using the functions given above?
```{r multiplication, exercise=TRUE}

```

```{r multiplication-hint}
s=1
for (i in 1:100) {
  
}
```

### b) 1 − 2 + 3 − 4 + 5 − .... − 100 =?

Try to solve this using a loop

```{r add-subtract, exercise=TRUE}

```

You can also try doing this question with seq() and sum() without using loop.
```{r add-subtract-additional, exercise=TRUE}

```



### c) 110 + 120 + 130 + ... + 500 =?

```{r sum-hundred, exercise=TRUE}

```

You can also try doing this question with seq() and sum() without using loop.



### d).\[
\sum_{i=1}^{100} i^3
\]

```{r sum-hundred-additional, exercise=TRUE}

```

### e).Find the maximum value of N for which 1 + 2 + 3 + ... + N < 4000.

\(\frac{{(1 + N) \cdot N}}{2} = 4000\)

\((1 + N) \cdot N = 8000\)

\(N^2 + N - 8000 = 0\)

Recall that the quadratic function can be solved by the formula

\[ x = \frac{{-b \pm \sqrt{{b^2 - 4ac}}}}{{2a}} \]

here, a = 1, b=1, c=-8000

```{r max-verify,exercise=TRUE, exercise.eval=TRUE}
a = 1
b=1
c=-8000
(-b+sqrt(b^2-4*a*c))/2*a
(-b-sqrt(b^2-4*a*c))/2*a
```
The second answer can be neglected since it is negative, based on the first output, the answer should be 88 or 89? Try to solve this question using for-loop or while loop and/or using if statement in the following chunk.

```{r max-index, exercise=TRUE}

```
