---
title: "Week-1 Interactive Practice"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```


## Topic 1: Quiz




```{r quiz1}
quiz(
  question("In which of the following panes the information of created objects such as scalars, vectors or
data-sets, in any session show up?",
    answer("source",message = "The source pane is where you can open/edit code files and save for future use."),
    answer("console",message =  "The console is where you can type in the codes and where R prints the numeric outputs."),
    answer("Environment", correct = TRUE),
    answer("Plots/Help/Files", message = "The Plots/Help/Files pane is where you can toggle between any graphical output,
help pages, or file directories."),
    allow_retry = TRUE
  )
)
```



## Topic 2: for-loop

### a) 1 ∗ 2 ∗ 3 ∗ 4 ∗ ..... ∗ 10 =?

We all know that this is actually 10! and computed by the following expression in r.
```{r factorial,echo=T}
factorial(10)
```

How can we compute this using a for-loop?
```{r multiplication, exercise=TRUE}

```

```{r multiplication-hint}
s=1
for (i in 1:10) {
  
}
```

### b) 1 − 2 + 3 − 4 + 5 − .... − 100 =?

Try to solve this using a for-loop and an if() statement inside the loop

```{r add-subtract, exercise=TRUE}

```


```{r add-subtract-hint}
# this following line checks if "i" is divisible by 2 or not
(i%%2)==0
```





## Topic 3: while-loop

### e) Find the maximum value of N for which 1 + 2 + 3 + ... + N < 4000.

The answer is 88.

\  


Try to find this using a while-loop. Your loop should keep adding as long as the cumulative sum does not exceed 4000.

```{r max-index, exercise=TRUE}

```
