---
title: "Week-7 Interactive Practice"
author: "Created by: Congyu Hang and Shahriar Shams"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```

## Testing Hypothesis


### a). 
In this question we will use the data set iris. Please plot the following density curve of *Sepal.Width* with respect to each species using different.

```{r, message = FALSE, echo=FALSE}
library(tidyverse)
data("iris")
ggplot(iris,aes(Sepal.Width)) + geom_density(aes(fill=factor(Species)),alpha=0.5)
```

```{r w71,exercise=TRUE}
library(tidyverse)
data("iris")
#data set iris is loaded
```


```{r w71-hint}
#ggplot(...) + geom_density(aes(fill=...))
```



### b). 
We can observe that the distribution of *virginica's Sepal.Width* looks normal and based on results from Shapiro Wilk test (test of Normality, you can check this link if you're interested https://builtin.com/data-science/shapiro-wilk-test), we can assume the data is Normal and conduct further testing. 

\[\text{Null Hypothesis (H0): } \mu = 3\]

\[\text{Alternative Hypothesis (H1): } \mu \neq 3\]

Confidence Level = 90%

Please conduct the 2-sided test using the built-in function and interpret your result using p-value and confidence interval.
Hint: You need to filter and select the data you need to do hypothesis testing.


```{r w72,exercise=TRUE}
library(tidyverse)
data("iris")

```


```{r w72-hint}
#... iris %>% filter(...Species == "virginica")
#t.test(...)
```


### c). Multiple Choice
t.test(width,mu=3,conf.level = 0.9)
```{r quiz1}
quiz(
  question("Which of the following code would generate same p-value from the previous testing code?",
    answer("t.test(width,mu=3,conf.level = 0.95)",correct=TRUE),
    answer("t.test(width,mu=3,alternative='greater',conf.level = 0.9)"),
    answer("t.test(width,mu=3,alternative='less',conf.level = 0.9)"),
    answer("t.test(width,mu=2,conf.level = 0.9)"),
    allow_retry = TRUE
  )
)
```
### d).

Please use bootstrapping to generate p-value of

\[\text{Null Hypothesis (H0): } \mu = 3\]

\[\text{Alternative Hypothesis (H1): } \mu \neq 3\]

```{r w73,exercise=TRUE}
library(tidyverse)
data("iris")

```


```{r w73-hint}
# mu_H0 = ...
# obs_mean = ...
# center the samples around mu_H0
# boot_func = function(){...}
# boot_new_x_bar = replicate(...)
# Hint: calculating 2-sided p-value
# mean(abs(boot_new_x_bar-mu_H0)>abs(obs_mean-mu_H0))
```

