---
title: "Week-8 Interactive Practice"
author: "Created by: Congyu Hang and Shahriar Shams"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```


## Comparison between Populations


### a).

Please extract data of Asia and Africa for the year of 1997 from gapminder table and plot the following density curve of these 2 continents with the variable *lifeExp*

```{r,message = FALSE,echo=FALSE}
library(tidyverse)
library(gapminder)
d = gapminder %>% dplyr::filter(continent %in% c( "Asia","Africa") & year == 1997)
ggplot(d, aes(x = lifeExp,fill=continent))+geom_density(alpha=0.5)
```


```{r w81,exercise=TRUE}
library(tidyverse)
library(gapminder)
```


```{r w81-hint}
#plot(...)
#lines(...)
```

\  

\  


### b).
Assume the 2 populations follow normal distribution.
Compare the variances of *lifeExp* at 1997 in Asia and Africa at 99% confidence level.


```{r w82,exercise=TRUE}
library(tidyverse)
library(gapminder)
```


```{r w82-hint}
#var.test(...)
```

\  
\  



### c).

Based on the result from part b), using an appropriate test, test the equality of the means of these 2 populations at 99% confidence level.

```{r w83,exercise=TRUE}
library(tidyverse)
library(gapminder)
```

```{r w83-hint}
#t.test(...)
```

\  
\  


### d).

Conduct a paired t-test to test the equality of the mean of *lifeExp* of all countries between 1952 and 1957. Try constructing a wide table and then do the paired t-test.

```{r w85,exercise=TRUE}
library(tidyverse)
library(gapminder)
```

```{r w85-hint}
#pd = gapminder %>% select(...) %>% filter(...)
#d2.wide = pd %>% pivot_wider(...)
#t.test(...)
```


\  

\  

### e).
By using the dataset from part (a), conduct a permutation test to test the equality of the two means (i.e. for Asia and Africa).

```{r w84,exercise=TRUE}
library(tidyverse)
library(gapminder)
```

```{r w84-hint}
#obs.diff = ...
#perm.function = function(){
  #temp_group_ind =
  #d =...
#}

#perm_diff = replicate(...)
```

